---
title: "ushorror"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ushorror}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# Load the necessary libraries
library(UShorrorsite)
library(dplyr)
library(ggplot2)
haunted_data
```


# Introduction
# This vignette provides an overview of how to work with the `haunted_data` dataset.
# Demonstrate some common operations, such as calculating the proportion of hauntings
# at each location within a city and visualizing the most haunted locations.

#' ## Loading and Inspecting the Data
```{r}

# Display the first few rows of `haunted_data`
head(haunted_data)
```


```{r}
#' ## Calculating Proportions of Hauntings by Location

# We can use the `location_proportions` function to calculate the proportion of hauntings for each location within a specific city.
# Here’s how to use it for a specific city, say `"Washington"`.

location_proportions(haunted_data, city = "Washington")

# Alternatively, we can calculate proportions across all cities if we want a broader view.
location_proportions(haunted_data)

```


#' ## Visualizing the Most Haunted Locations in a City

```{r}
# creating a bar plot to visualize the most haunted locations within a selected city.
# visualize hauntings in `"Washington"`.

# Filter for the selected city
city_data <- haunted_data %>%
  filter(city == "Washington") %>%
  count(location, sort = TRUE)

# Plot the most haunted locations in Washington
ggplot(city_data, aes(x = reorder(location, n), y = n)) +
  geom_bar(stat = "identity", fill = "darkred") +
  coord_flip() +
  labs(title = "Most Haunted Locations in Washington",
       x = "Location",
       y = "Number of Hauntings") +
  theme_minimal()
```



#' ## Summary Statistics for a City

```{r}
# Calculating some summary statistics, such as the most haunted location, the total number of hauntings,
# and the average number of hauntings per location in a given city, such as `"Washington"`.

city_data <- haunted_data %>%
  filter(city == "Washington") %>%
  count(location, sort = TRUE)

# Most haunted location
most_haunted <- city_data$location[1]

# Total number of hauntings
total_hauntings <- sum(city_data$n)

# Average hauntings per location
avg_hauntings <- mean(city_data$n)

# Display the summary
cat("Summary for Washington:\n",
    "- Most haunted location:", most_haunted, "\n",
    "- Total number of hauntings:", total_hauntings, "\n",
    "- Average hauntings per location:", round(avg_hauntings, 2), "\n")
```


#' ## Conclusion
# This vignette has demonstrated basic operations for exploring the `haunted_data` dataset,
# calculating proportions, and visualizing the most haunted locations. You can use these 
# techniques to analyze haunted locations in other cities or perform similar operations on similar datasets.

